---
title: "Diversity Project Abundances"
author: "Joshua"
date: "4/1/2021"
output:
  pdf_document: default
  html_document: default
---

```{r}
rm(list=ls())
dev.off ()
package.list <- c('vegan', 'data.table', 'reshape2', 'ggplot2', 'ape')
for (package in package.list){
  if (!require(package, character.only = TRUE, quietly = TRUE)) {
    install.packages(package)
    library(package,character.only = TRUE)
  }
}
```

# Importing site-species data into R

```{r}
site_species <- read.csv("alpine_ridge_data/OTU_table.csv", header = TRUE)
site_species.t <- t(site_species)
```

#Rarefaction

```{r}
#Visualization of rarecurves for all samples
richness <- rowSums((site_species.t > 0) * 1)
print(richness)
minimum.r <- min(rowSums(site_species.t))
rarefy <- rarefy(x = site_species.t, sample = minimum.r, se = TRUE)

rarecurve(x = site_species.t, step = 20, col = "blue", cex = .6, las = 1)
abline(0, 1, col = 'red')
text(200, 100, "1:1", pos = 2, col = 'red')
```

```{r}
#Rarefaction of samples
site_species.r <- rrarefy(site_species.t, 1000)

richness <- rowSums((site_species.r > 0) * 1)
minimum.r <- min(rowSums(site_species.r))
rarefy <- rarefy(x = site_species.r, sample = minimum.r, se = TRUE)

rarecurve(x = site_species.r, step = 20, col = "blue", cex = .6, las = 1)
abline(0, 1, col = 'red')
text(200, 100, "1:1", pos = 2, col = 'red')
```

```{r}
#Remove samples containing less than 1000 reads (R1.14, R1.55.2, R2.25, S2.78.2)

df.site_species.r <- as.data.frame(site_species.r)
rarefied_site_species <- data.frame()

for (i in 1:nrow(df.site_species.r)){
  if (rowSums(df.site_species.r[i,]) >= 1000){
    rarefied_site_species <- rbind(rarefied_site_species, df.site_species.r[i,])
  }
}

#Visualizing
richness <- rowSums((rarefied_site_species > 0) * 1)
minimum.r <- min(rowSums(rarefied_site_species))
rarefy <- rarefy(x = rarefied_site_species, sample = minimum.r, se = TRUE)

rarecurve(x = rarefied_site_species, step = 20, col = "blue", cex = .6, las = 1)
abline(0, 1, col = 'red')
text(200, 100, "1:1", pos = 2, col = 'red')
```


#Removing samples to match environmental data downstream

```{r}
rarefied_site_species <- rarefied_site_species[-c(38,43,48),]
```


# Importing Environmental Data

```{r}
env <- read.csv("alpine_ridge_data/variables.txt", header = TRUE, sep = "\t")
env <- env[-c(26,31),]
```


# Calculating Bray-Curtis Beta-Diversity 

```{r}
fungalBC <- vegdist(rarefied_site_species, method = "bray")
```


# Cluster Analysis of Fungal Communities

```{r} 
#Performing Cluster Analysis
fungal.ward <- hclust(fungalBC, method = "ward.D2")

#Plotting Cluster
par(mar = c(1,5,2,2) + .1)
plot(fungal.ward, main = "Doubs River Fish: Ward's Clustering",
     ylab = "Squared Bray-Curtis Distance")
```


# PCoA of Fungal Communities

```{r}
fungal.pcoa <- cmdscale(fungalBC, eig = TRUE, k = 3)

explainvar1 <- round(fungal.pcoa$eig[1]/sum(fungal.pcoa$eig), 3) * 100
explainvar2 <- round(fungal.pcoa$eig[2]/sum(fungal.pcoa$eig), 3) * 100
explainvar3 <- round(fungal.pcoa$eig[3]/sum(fungal.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

test <- rarefied_site_species

test$Site <- c(rep("S1", 5), rep("S2", 5), rep("S3", 5), rep("S4", 5), rep("S5", 5), rep("R1", 4), rep("R2", 4), rep("R3", 5), rep("R4", 5), rep("R5", 5))

test$Location <- c(rep("Snowbed", 25), rep("Ridge", 23))

## Plotting
# make a fake pcoa
dist      <- vegdist(test[,1:807],  method = "bray")
fake_pcoa <- pcoa(dist)
#summary(fake_pcoa) 

# get the out of pcoa 
# site scores = samples 
sitescores   <- fake_pcoa$vectors #we need only the first two axis 
newdata <- as.data.frame(cbind(sitescores[,1:2], Location = test$Location, Site = test$Site))

#one way 
bray <- ggplot(newdata, aes(y = as.numeric(Axis.1), x = as.numeric(Axis.2), shape = Location, color = Site))
bray <- bray + geom_hline(yintercept = 0, color = "grey", linetype = "dashed")
bray <- bray + geom_vline(xintercept = 0, color = "grey", linetype = "dashed")
bray <- bray + geom_point(size = 3, alpha = .5)
bray <- bray + theme_bw()
bray <- bray + labs(y = paste("PCoA 1 (", explainvar1, "%)", sep = ""), x = paste("PCoA 2 (", explainvar2, "%)", sep = ""))
bray
```

# How much variance is explained by site location (Bray-Curtis)

```{r}
site <- c(rep("S1", 5), rep("S2", 5), rep("S3", 5), rep("S4", 5), rep("S5", 5), rep("R1", 4), rep("R2", 4), rep("R3", 5), rep("R4", 5), rep("R5", 5))

adonis(rarefied_site_species ~ env$V + site, permutations = 999)

```


# Calculating Sorensen Beta-Diversity

```{r}
fungalS <- vegdist(rarefied_site_species, method = "bray", binary = "TRUE")
```


# Cluster Analysis of Fungal Communities

```{r} 
#Performing Cluster Analysis
fungal.wardS <- hclust(fungalS, method = "ward.D2")

#Plotting Cluster
par(mar = c(1,5,2,2) + .1)
plot(fungal.wardS, main = "Doubs River Fish: Ward's Clustering",
     ylab = "Squared Sørensen's Distance")
```

# PCoA of Fungal Communities

```{r}
fungal.S.pcoa <- cmdscale(fungalS, eig = TRUE, k = 3)

explainvar1 <- round(fungal.S.pcoa$eig[1]/sum(fungal.pcoa$eig), 3) * 100
explainvar2 <- round(fungal.S.pcoa$eig[2]/sum(fungal.pcoa$eig), 3) * 100
explainvar3 <- round(fungal.S.pcoa$eig[3]/sum(fungal.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

## Plotting
# make a fake pcoa
dist      <- vegdist(test[,1:807],  method = "bray", binary = TRUE)
fake_pcoa <- pcoa(dist)
#summary(fake_pcoa) 

# get the out of pcoa 
# site scores = samples 
sitescores   <- fake_pcoa$vectors #we need only the first two axis 
newdata <- as.data.frame(cbind(sitescores[,1:2], Location = test$Location, Site = test$Site))

#one way 
soren <- ggplot(newdata, aes(y = as.numeric(Axis.1), x = as.numeric(Axis.2), shape = Location, color = Site))
soren <- soren + geom_hline(yintercept = 0, color = "grey", linetype = "dashed")
soren <- soren + geom_vline(xintercept = 0, color = "grey", linetype = "dashed")
soren <- soren + geom_point(size = 3, alpha = .5)
soren <- soren + theme_bw()
soren <- soren + labs(y = paste("PCoA 1 (", explainvar1, "%)", sep = ""), x = paste("PCoA 2 (", explainvar2, "%)", sep = ""))
soren
```


# How much variance is explained by site location (Sorensen)

```{r}
site <- c(rep("S1", 5), rep("S2", 5), rep("S3", 5), rep("S4", 5), rep("S5", 5), rep("R1", 4), rep("R2", 4), rep("R3", 5), rep("R4", 5), rep("R5", 5))

adonis(rarefied_site_species ~ env$V + site, method = "bray", binary = TRUE, permutations = 999)
```


## Relative Abundance Visualization

```{r}
genus <- read.csv("alpine_ridge_data/genus_table.csv", header = TRUE)
#convert rownames into column

genus.1 <- as.data.frame(t(rarefied_site_species))
setDT(genus.1, keep.rownames = TRUE)[]

# Converting to Long Format
genus_long <- melt(genus.1, id.vars = "rn", variable.name = "Sample")

# Creating Graph of data
genus_graph <- ggplot(data = genus_long, mapping = aes(x = Sample,  y = value, fill = rn))
genus_graph <- genus_graph + geom_bar(stat="identity")
genus_graph <- genus_graph + labs(y = "Relative Abundance", x = "Sample", title = "Genus Relative Abundances") + theme_classic()
genus_graph <- genus_graph + theme(legend.position = "None")
genus_graph <- genus_graph + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
genus_graph
```


# Importing environmental data and testing for significance 

```{r}
env <- read.csv("alpine_ridge_data/variables.txt", header = TRUE, sep = "\t")
env <- env[-c(26,31),]

site <- c(rep("S1", 5), rep("S2", 5), rep("S3", 5), rep("S4", 5), rep("S5", 5), rep("R1", 4), rep("R2", 4), rep("R3", 5), rep("R4", 5), rep("R5", 5))
adonis(rarefied_site_species ~ env$V + site, method = "bray", permutations = 999)
```


# Constructing Constrained Ordination

```{r}
env.chem <- as.matrix(env[,c(2:4)])


S.dbrda <- dbrda(fungalS ~ ., as.data.frame(env.chem))
ordiplot(S.dbrda)

S.dbrda0 <- dbrda(fungalS ~ 1, as.data.frame(env.chem))
S.dbrda1 <- dbrda(fungalS ~ ., as.data.frame(env.chem))

S.dbrda <- ordiR2step(S.dbrda0, S.dbrda1, perm.max = 999)

permutest(S.dbrda, permutations = 999)
envfit(S.dbrda, env.chem, permutations = 999)

#Calculating explained variation on axes
S.explainvar1 <- round(S.dbrda$CCA$eig[1]/
                             sum(c(S.dbrda$CCA$eig, S.dbrda$CA$eig)),
                           3 ) * 100
S.explainvar2 <- round(S.dbrda$CCA$eig[2]/
                             sum(c(S.dbrda$CCA$eig, S.dbrda$CA$eig)),
                           3 ) * 100

#Plotting constrained ordination results
par(mar = c(5,5,4,4) + .1)

plot(scores(S.dbrda, display = "wa"), xlim = c(-2, 2.1), ylim = c(-2.3, 2.0), 
     xlab = paste("dbRDA 1 (", S.explainvar1, "%)", sep = ""),
     ylab = paste("dbRDA 2 (", S.explainvar2, "%)", sep = ""),
     pch = 16, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, axes = FALSE
     )

axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

points(scores(S.dbrda, display = "wa"),
       pch = 19, cex = 3, bg = "gray", col = "gray")
text(scores(S.dbrda, display = "wa"),
     labels = row.names(scores(S.dbrda, display = "wa")))

#Plotting vectors for influence of environmental factors
vectors <- scores(S.dbrda, display = "bp")
arrows(0, 0, vectors[,1], vectors[,2],
       lwd = 2, lty = 1, length = .2, col = "red")
text(vectors[,1], vectors[,2], pos = 3, 
     labels = row.names(vectors), col = "red")
axis(side = 3, lwd.ticks = 2, cex.axis = 1.2, las = 1, col = "red", lwd = 2.2,
     at = pretty(range(vectors[,1])) * 2, labels = pretty(range(vectors[,1])))
axis(side = 4, lwd.ticks = 2, cex.axis = 1.2, las = 1, col = "red", lwd = 2.2,
     at = pretty(range(vectors[,2])) * 2, labels = pretty(range(vectors[,2])))
```



```{r}
env.chem <- as.matrix(env[,c(2:4)])

fungalS <- fungalBC

S.dbrda <- dbrda(fungalS ~ ., as.data.frame(env.chem))
ordiplot(S.dbrda)

S.dbrda0 <- dbrda(fungalS ~ 1, as.data.frame(env.chem))
S.dbrda1 <- dbrda(fungalS ~ ., as.data.frame(env.chem))

S.dbrda <- ordiR2step(S.dbrda0, S.dbrda1, perm.max = 999)
```
Sorensen distance is influenced by Nitrogen concentration in the soil but BC is not influenced by Nitrogren, Carbon, or Phosphorus 


# Effect of plant abundance and diversity on fungal community structure

```{r}
# Making new dataframe with summary of all statistics
plot.info <- as.data.frame(matrix(nrow = 10, ncol=1))
plot.info <- plot.info[,-1]
plot.info$Location <- c(rep("Ridge", 5), rep("Snowbed", 5))
rownames(plot.info) <- c("S1","S2","S3","S4","S5","R1","R2","R3","R4","R5")
plot.info$site <- c("S1","S2","S3","S4","S5","R1","R2","R3","R4","R5")

# Adding average soil nutrients
plot.info$P <- c(mean(env[1:5, 2]), mean(env[6:10, 2]), mean(env[11:15, 2]), mean(env[16:20, 2]), mean(env[21:25, 2]), mean(env[26:29, 2]),mean(env[30:33, 2]), mean(env[34:38, 2]), mean(env[39:43, 2]), mean(env[44:48, 2]))
plot.info$N <- c(mean(env[1:5, 3]), mean(env[6:10, 3]), mean(env[11:15, 3]), mean(env[16:20, 3]), mean(env[21:25, 3]), mean(env[26:29, 3]),mean(env[30:33, 3]), mean(env[34:38, 3]), mean(env[39:43, 3]), mean(env[44:48, 3]))
plot.info$C <- c(mean(env[1:5, 4]), mean(env[6:10, 4]), mean(env[11:15, 4]), mean(env[16:20, 4]), mean(env[21:25, 4]), mean(env[26:29, 4]),mean(env[30:33, 4]), mean(env[34:38, 4]), mean(env[39:43, 4]), mean(env[44:48, 4]))

# Adding alpha diversity data
rarefied.sites <- as.data.frame((matrix(nrow = 10, ncol = 807)))
for (i in 1:(ncol(rarefied_site_species))){
  rarefied.sites[,i] <- c(sum(rarefied_site_species[1:5, i]), sum(rarefied_site_species[6:10, i]), sum(rarefied_site_species[11:15, i]), sum(rarefied_site_species[16:20, i]), sum(rarefied_site_species[21:25, i]), sum(rarefied_site_species[26:29, i]),sum(rarefied_site_species[30:33, i]), sum(rarefied_site_species[34:38, i]), sum(rarefied_site_species[39:43, i]), sum(rarefied_site_species[44:48, i]))
}
rownames(rarefied.sites) <- c("S1","S2","S3","S4","S5","R1","R2","R3","R4","R5")

# Species richness
plot.info$richness <- rowSums((rarefied.sites > 0) * 1)


plot.info <- as.data.frame(plot.info)
```

# PCoA of Grouped Fungal Communities

#Site-grouped Bray-Curtis
```{r}
fungalBC <- vegdist(rarefied.sites, method = "bray")

fungal.pcoa <- cmdscale(fungalBC, eig = TRUE, k = 3)

explainvar1 <- round(fungal.pcoa$eig[1]/sum(fungal.pcoa$eig), 3) * 100
explainvar2 <- round(fungal.pcoa$eig[2]/sum(fungal.pcoa$eig), 3) * 100
explainvar3 <- round(fungal.pcoa$eig[3]/sum(fungal.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

test <- rarefied.sites

test$Site <- c("S1","S2","S3","S4","S5","R1","R2","R3","R4","R5")

test$Location <- c(rep("Ridge", 5), rep("Snowbed", 5))

## Plotting
# make a fake pcoa
dist      <- vegdist(test[,1:807],  method = "bray")
fake_pcoa <- pcoa(dist)
#summary(fake_pcoa) 

# get the out of pcoa 
# site scores = samples 
sitescores   <- fake_pcoa$vectors #we need only the first two axis 
newdata <- as.data.frame(cbind(sitescores[,1:2], Location = test$Location, Site = test$Site))

#one way 
bray <- ggplot(newdata, aes(y = as.numeric(Axis.1), x = as.numeric(Axis.2), shape = Location, color = Site))
bray <- bray + geom_hline(yintercept = 0, color = "grey", linetype = "dashed")
bray <- bray + geom_vline(xintercept = 0, color = "grey", linetype = "dashed")
bray <- bray + geom_point(size = 3, alpha = .5)
bray <- bray + theme_bw()
bray <- bray + labs(y = paste("PCoA 1 (", explainvar1, "%)", sep = ""), x = paste("PCoA 2 (", explainvar2, "%)", sep = ""))
bray
```

```{r}
#Performing Cluster Analysis
fungal.ward <- hclust(fungalBC, method = "ward.D2")

#Plotting Cluster
par(mar = c(1,5,2,2) + .1)
plot(fungal.ward, main = "Doubs River Fish: Ward's Clustering",
     ylab = "Squared Sørensen's Distance")
```

# Site-grouped Sorensen
```{r}
fungalBC <- vegdist(rarefied.sites, method = "bray", binary = TRUE)

fungal.pcoa <- cmdscale(fungalBC, eig = TRUE, k = 3)

explainvar1 <- round(fungal.pcoa$eig[1]/sum(fungal.pcoa$eig), 3) * 100
explainvar2 <- round(fungal.pcoa$eig[2]/sum(fungal.pcoa$eig), 3) * 100
explainvar3 <- round(fungal.pcoa$eig[3]/sum(fungal.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

test <- rarefied.sites

test$Site <- c("S1","S2","S3","S4","S5","R1","R2","R3","R4","R5")

test$Location <- c(rep("Ridge", 5), rep("Snowbed", 5))

## Plotting
# make a fake pcoa
dist      <- vegdist(test[,1:807],  method = "bray", binary = TRUE)
fake_pcoa <- pcoa(dist)
#summary(fake_pcoa) 

# get the out of pcoa 
# site scores = samples 
sitescores   <- fake_pcoa$vectors #we need only the first two axis 
newdata <- as.data.frame(cbind(sitescores[,1:2], Location = test$Location, Site = test$Site))

#one way 
bray <- ggplot(newdata, aes(y = as.numeric(Axis.1), x = as.numeric(Axis.2), shape = Location, color = Site))
bray <- bray + geom_hline(yintercept = 0, color = "grey", linetype = "dashed")
bray <- bray + geom_vline(xintercept = 0, color = "grey", linetype = "dashed")
bray <- bray + geom_point(size = 3, alpha = .5)
bray <- bray + theme_bw()
bray <- bray + labs(y = paste("PCoA 1 (", explainvar1, "%)", sep = ""), x = paste("PCoA 2 (", explainvar2, "%)", sep = ""))
bray
```

```{r}
#Performing Cluster Analysis
fungal.ward <- hclust(fungalBC, method = "ward.D2")

#Plotting Cluster
par(mar = c(1,5,2,2) + .1)
plot(fungal.ward, main = "Doubs River Fish: Ward's Clustering",
     ylab = "Squared Bray-Curtis Distance")
```

```{r}
env.chem <- as.matrix(plot.info[,3:5])

fungalS <- fungalBC

S.dbrda <- dbrda(fungalS ~ ., as.data.frame(env.chem))
ordiplot(S.dbrda)

S.dbrda0 <- dbrda(fungalS ~ 1, as.data.frame(env.chem))
S.dbrda1 <- dbrda(fungalS ~ ., as.data.frame(env.chem))

S.dbrda <- ordiR2step(S.dbrda0, S.dbrda1, perm.max = 999)


```

```{r}
plant <- read.csv("alpine_ridge_data/veg.csv")
plant <- t(plant)
colnames(plant) <- plant[1,]
plant <- plant[-1,]

plot.info$num.rock <- plant[,49]
plant <- plant[,-c(48,49)]

plant.num <- as.data.frame(matrix(nrow = 10, ncol = 47))
colnames(plant.num) <- colnames(plant)
rownames(plant.num) <- rownames(plant)

for (i in 1:ncol(plant)){
  plant.num[,i] <- c(as.numeric(plant[,i]))
}


plot.info$plant.richness <- rowSums((plant.num > 0) * 1)

library(lmerTest)
library(car)
#richness.lm <- lm(data = plot.info, richness ~ C + P + N + num.rock + plant.richness)
#summary(richness.lm)
# mixed model
#richness.lm <- lmer(data = plot.info, richness ~ C + P + N+ (1|num.rock))
#anv <- Anova(richness.lm, type = "III")
#print(anv)
# with plant richness mixed model
#richness.lm.1 <- lmer(data = plot.info, richness ~ C * P * N * plant.richness + (1|num.rock))
#anv.1 <- Anova(richness.lm, type = "III")
#print(anv.1)
# fixed model
richness.lm.fixed <- lm(data = plot.info, richness ~ C + P + N + plant.richness)
summary(richness.lm.fixed)
anv.fixed <- Anova(richness.lm.fixed, type = "III")
print(anv.fixed)
# with plant richness model
#richness.lm.fixed <- lm(data = plot.info, richness ~ C + P + N + site + plant.richness + Location + C:P + C:N + P:N + plant.richness + plant.richness:N + plant.richness:C + plant.richness:P )
#summary(richness.lm.fixed)
#anv.fixed <- Anova(richness.lm.fixed, type = "III")
#print(anv.fixed)
# fixed model
#richness.lm.fixed <- lm(data = plot.info, richness ~ C + P + N + Location)
#anv.fixed <- Anova(richness.lm.fixed, type = "III")
#print(anv.fixed)
```

```{r}
average <- as.data.frame(matrix(nrow = 1, ncol = 807))


for (i in 1:ncol(rarefied_site_species)){
  average[,i] <- mean(rarefied_site_species[,i])
}

colnames(average) <- c(genus[,1])

average <- t(average)
average <- as.data.frame(average)

average$num <- c(1:807)
```

```{r}
# Soil chemistry across snowbed vs ridge

rownames(env) <- c(1:48)
env.comp <- as.data.frame(matrix(nrow = 2, ncol = 6))
rownames(env.comp) <- c("Snowbed","Ridge")
colnames(env.comp) <- c("P.Mean","P.std.error","N.Mean","N.std.error","C.Mean","C.std.error")

#Calculating means
env.comp$P.Mean <- c(mean(env[1:25,2]),mean(env[26:48,2]))
env.comp$N.Mean <- c(mean(env[1:25,3]),mean(env[26:48,3]))
env.comp$C.Mean <- c(mean(env[1:25,4]),mean(env[26:48,4]))

#Calculating standard error
sem <- function(x){
  sd(x)/sqrt(length(x))
  }

env.comp$P.std.error <- c(sem(env[1:25,2]),sem(env[26:48,2]))
env.comp$N.std.error <- c(sem(env[1:25,3]),sem(env[26:48,3]))
env.comp$C.std.error <- c(sem(env[1:25,4]),sem(env[26:48,4]))

env.data <- as.data.frame(matrix(nrow = 6, ncol = 4))
colnames(env.data) <- c("Mean","std.error","element", "site")
env.data$element <- c('P','P','N','N','C','C')
env.data$site <- c('R','S','R','S','R','S')
env.data$Mean <- c(env.comp[2,1],env.comp[1,1],env.comp[2,3],env.comp[1,3],env.comp[2,5],env.comp[1,5])
env.data$std.error <- c(env.comp[2,2],env.comp[1,2],env.comp[2,4],env.comp[1,4],env.comp[2,6],env.comp[1,6])
```

```{r}
env.plot <- ggplot(env.data, aes(x = element, y = Mean, color = site))
env.plot <- env.plot + geom_point()
env.plot
print(env.plot)
```


```{r}
richnesses <- as.data.frame(matrix(nrow = 20, ncol = 3))
colnames(richnesses) <- c('richness','sample','site')

richnesses$richness <- c(plot.info$richness, plot.info$plant.richness)
richnesses$sample <- c(rep("fungal", 10), rep("plant", 10))
richnesses$site <- c("S1","S2","S3","S4","S5","R1","R2","R3","R4","R5")
```

```{r}
rich <- ggplot(data = richnesses, aes(x = site, y = richness, shape = sample))
rich <- rich + geom_point(aes(size = 4))
rich <- rich + theme_classic()
print(rich)
```

```{r}
lmc <- lm(N ~ site, data = plot.info)
anvc <- anova(lmc)
print(anvc)
```

```{r}
genus.1 <- as.data.frame(rarefied_site_species)
colnames(genus.1) <- genus$Genus
genus.1 <- t(genus.1)
rownames(genus.1) <- c(1:nrow(genus.1))

major.taxa <- c(219, 419, 89, 708, 176, 68, 493, 222, 489, 468)

genus.2 <- as.data.frame(matrix(nrow = 10, ncol = 807))
colnames(genus.2) <- colnames(genus.1)
genus.2 <- genus.1[c(major.taxa),]
rownames(genus.2) <- genus[c(major.taxa),1]

#setDT(genus.1, keep.rownames = TRUE)[]
#genus.1$taxa <- rownames(genus.1)

#imp.fung <- c("Russula.3", "X.Phialocephala.15", "X.Cortinarius.12", "X.Articulospora.23", "unknown.50", "X.Laccaria.1", "unknown.175", "Russula.6", "X.Lachnum.4", "X.Articulospora.6")

#genus.2 <- as.data.frame(matrix(nrow = 0, ncol = 48))
#for (i in 1:nrow(genus.1)){
#  if (rownames(genus.1[i,]) == imp.fung){
#    genus.2[(nrow(genus.2) + 1),] <- genus.1[i,]
#  }
#}
#colnames(genus.2) <- colnames(genus.1)

# Converting to Long Format
genus_long <- melt(genus.2, id.vars = "rn", variable.name = "Sample")
colnames(genus_long) <- c("Genus", "Sample", "Abundance")

# Creating Graph of data
genus_graph <- ggplot(data = genus_long, mapping = aes(x = Sample,  y = Abundance, fill = Genus))
genus_graph <- genus_graph + geom_bar(stat="identity")
genus_graph <- genus_graph + labs(y = "Abundance", x = "Sample", title = "Relative Abundance of top 10 Genera") + theme_classic()
#genus_graph <- genus_graph + theme(legend.position = "None")
genus_graph <- genus_graph + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
genus_graph
```
